manuscript

### 2021-02-27 reports/manuscript.Rmd
Updates manuscript

@@

df_rbans_long %>%
  filter(grepl("dim_", subtest)) %>%
  group_by(subtest, diagnosis) %>%
  summarise(mean = mean(z_score, na.rm = TRUE)) %>%
  pivot_wider(names_from = diagnosis, values_from = mean) %>%
  right_join(df_diag_difference, by = "subtest") %>%
  knitr::kable(digits = 3)
```

@@

df_temp <- df_questionnaire_long %>%
  group_by(question_area, question_focus) %>%
  summarise(mean = mean_and_sd_report(score)) %>%
  pivot_wider(names_from = question_focus, values_from = mean)

@@

```{r}
df_results_remediation %>%
  group_by(session, n_items) %>%
  summarise(correct_ratio = mean_and_sd_report(correct_ratio),
            time = mean_and_sd_report(results_time),
            trajectory = mean_and_sd_report(results_trajectory)) %>%
  filter(session == 2 | session == 12) %>%
  knitr::kable(caption = "Select what might be relevant or what to aggregate together")
```

@@

lmer_time_session_trial <- lmer(results_time ~ session + n_items + (1|participant), data = df_results_remediation)

lmer_trajectory_session_trial <- lmer(results_trajectory ~ session + n_items + (1|participant), data = df_results_remediation)

lmer_correct_session_6_9 <- lmer(correct_ratio ~ session + n_items + (1|participant), data = filter(df_results_remediation, n_items >= 6))
```

@@

```{r}
df_rbans %>%
  group_by(session, trenink) %>%
  summarise_at(vars(starts_with("dim")), list(desc = mean_and_sd_report,
            n = ~sum(!is.na(.x)))) %>%
  mutate(number = dim_kratkodobapamet_n) %>%
  select(-ends_with("_n")) %>%
  rename_with(~gsub("dim_(.*)_desc", "\\1", .x)) %>%
  knitr::kable()
```

@@

>>>>

We have observed that patients suffering from schizophrenia had significantly worse baseline RBANS performance than patietns with affective disorders (see table XXX). This was one of the reasons we opted for the linear mixed modelling in our subsequent analyses as they should be able to control for the effect of diagnosis.

@@

df_rbans_long %>%
  filter(grepl("dim_", subtest), session == 1) %>%
  group_by(subtest, diagnosis) %>%
  summarise(m = mean_and_sd_report(z_score, type = "parentheses")) %>%
  pivot_wider(names_from = diagnosis, values_from = m) %>%
  right_join(df_diag_difference, by = "subtest") %>%
  knitr::kable(digits = 3)
```

@@

df_temp <- df_questionnaire_long %>%
  group_by(question_area, question_focus) %>%
  summarise(mean = mean_and_sd_report(score, type = "parentheses")) %>%
  pivot_wider(names_from = question_focus, values_from = mean)

@@

```{r}
df_results_remediation %>%
  group_by(session, n_items) %>%
  summarise(correct_ratio = mean_and_sd_report(correct_ratio, type="parentheses"),
            time = mean_and_sd_report(results_time, type="parentheses"),
            trajectory = mean_and_sd_report(results_trajectory, type="parentheses")) %>%
  filter(session == 2 | session == 12) %>%
  knitr::kable(caption = "Select what might be relevant or what to aggregate together")
```

@@

lmer_time_session_trial <- lmer(results_time ~ session + n_items + (1|participant), data = df_results_remediation)
lmer_trajectory_session_trial <- lmer(results_trajectory ~ session + n_items + (1|participant), data = df_results_remediation)
lmer_correct_session_6_9 <- lmer(correct_ratio ~ session + n_items + (1|participant), data = filter(df_results_remediation, n_items >= 6))
```

@@

```{r}
df_rbans %>%
  group_by(session, trenink) %>%
  summarise_at(vars(starts_with("dim")), list(
            desc = ~mean_and_sd_report(.x, type = "parentheses"),
            n = ~sum(!is.na(.x)))) %>%
  mutate(number = dim_kratkodobapamet_n) %>%
  select(-ends_with("_n")) %>%
  rename_with(~gsub("dim_(.*)_desc", "\\1", .x)) %>%
  knitr::kable()
```

@@

```{r session model explanation,eval = FALSE}
temp_mixed_func <- function(varname){
  out <- df_rbans_long %>%
    filter(subtest == varname) %>%
    lmer(z_score ~ factor(session) + (1|rbansid), data = .)
  return(out)
}

dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), 2)})
knitr::kable(as.data.frame(res),
             caption = "Trenink as a predictor of RBANS performance. Coefficients are for VR in contrast to TP (negative = VR does worse)")

df_rbans_long %>%
  filter(subtest == "dim_celek") %>%
  mutate(session = paste0("session ", session - 1)) %>%
  ggplot(aes(session, z_score, fill = trenink)) +
    geom_boxplot() +
    geom_jitter(position = position_dodge(width = 0.5)) +
    scale_fill_discrete(labels = c("baseline", "TP" = "Standard treatment", "VR" = "VEs program")) +
    geom_hline(yintercept = 0.07) +
    theme_apa() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = c(0.5,1), legend.direction = "horizontal") +
    labs(x = "", y = "Standardized score",
         title = "Standardized scores of RBANS cognitive domains",
         fill = "")

df_rbans_long %>%
  filter(subtest == "dim_celek") %>%
  ggplot(aes(session, z_score, group = rbansid)) + 
    geom_line() + geom_point(aes(color = trenink), size = 3)

df_rbans_long %>%
  filter(subtest == "dim_celek") %>%
  group_by(session) %>%
  summarise(mean_and_sd_report(score))
```
